### 2018-12-05 reports/thesis/book.tex
Added multiple hypothesis test section.
Adjusted harshness in NoDefect_Sinusoid, proof read inference chapter.
Started on empirical null filter subsection

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}

@@

\DeclareMathOperator{\expfamily}{ExpFamily}
\DeclareMathOperator{\expectation}{\mathbb{E}}
\DeclareMathOperator{\variance}{\mathbb{V}ar}
\DeclareMathOperator{\cov}{\mathbb{C}ov}
\DeclareMathOperator{\corr}{\mathbb{C}orr}
\DeclareMathOperator{\bernoulli}{Bernoulli}
\DeclareMathOperator{\betaDist}{Beta}
\DeclareMathOperator{\dirichlet}{Dir}
\DeclareMathOperator{\bin}{Bin}
\DeclareMathOperator{\MN}{Multinomial}
\DeclareMathOperator{\prob}{\mathbb{P}}
\DeclareMathOperator{\trace}{Tr}
\DeclareMathOperator{\normal}{N}
\DeclareMathOperator{\gammaDist}{Gamma}
\DeclareMathOperator{\poisson}{Poisson}
\DeclareMathOperator{\CPoisson}{CP\Gamma}
\DeclareMathOperator{\normDist}{N}

@@

\frontmatter
\section*{Abstract}
X-ray CT can be used for defect detection and quality control of 3D printing. This report will outline statistical methods for comparing x-ray scans of a 3D printed sample with its computer model under the face of uncertainty. Shading correction methods and the mean and variance relationship were investigated. Lastly the compound Poisson was reviewed.

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots

@@

\DeclareMathOperator{\expfamily}{ExpFamily}
\DeclareMathOperator{\expectation}{\mathbb{E}}
\DeclareMathOperator{\variance}{\mathbb{V}ar}
\DeclareMathOperator{\cov}{\mathbb{C}ov}
\DeclareMathOperator{\corr}{\mathbb{C}orr}
\DeclareMathOperator{\bernoulli}{Bernoulli}
\DeclareMathOperator{\betaDist}{Beta}
\DeclareMathOperator{\dirichlet}{Dir}
\DeclareMathOperator{\bin}{Bin}
\DeclareMathOperator{\MN}{Multinomial}
\DeclareMathOperator{\prob}{\mathbb{P}}
\DeclareMathOperator{\trace}{Tr}
\DeclareMathOperator{\normal}{N}
\DeclareMathOperator{\gammaDist}{Gamma}
\DeclareMathOperator{\poisson}{Poisson}
\DeclareMathOperator{\CPoisson}{CP\Gamma}
\DeclareMathOperator*{\argmax}{argmax}

@@

\frontmatter
\section*{Abstract}
X-ray computed tomography (CT) can be used for defect detection in 3D printing. The object is scanned at multiple angles to reconstruct the object in 3D space. The process can be time consuming. The aim of this project was to investigate if it is possible to conduct defect detection in projection space from a single scan to speed up the defect detection procedure. To do this, a 3D printed sample was manufactured with voids to see if they can be detected.

X-ray photons behave randomly. Hence to do defect detection pixel by pixel, uncertainty must be taken into account. A compound Poisson model was used to model the grey valyes in a pixel. It assumed that photon arrivals are a Poisson process with Gamma distributed energy. This resulted in a linear relationship between the mean and variance of the grey value, which was used for variance prediction and to quantify the uncertainty.

Software, called \texttt{aRTist}, was used to simulate the scan and it was compared with the x-ray acquisition under the face of uncertainty. However the software, and the information provided to it, was not perfect which led to model misspecification and incorrect inference. The empirical null filter was proposed. It adjust each pixel statistic so that inference was done by comparing each pixel with the majority of its local pixels.

### 2018-12-05 reports/thesis/chapters/5_inference.tex
Started on empirical null filter subsection

The empirical null filter is an extension to the empirical null. In this setting, the parameters of the empirical null varies spatially. Let $Z_{x,y}$ be the test statistic at position $(x,y)$ and
\begin{equation}
	Z_{x,y}|H_0\sim\normal\left(
		\mu_{x,y},\sigma_{0,x,y}^2
	\right)
	\ .
\end{equation}
Let the hypotheses
\begin{equation}
	H_0:\mu_{x,y}=\mu_{0,x,y}
\end{equation}
and
\begin{equation}
	H_1:\mu_{x,y}\neq\mu_{0,x,y}
\end{equation}
be tested for each pixel individually where $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the empirical null mean and standard deviation at position $(x,y)$ respectively. The empirical null filter aims to estimate these parameters.

The method is the following. A window size needs to be specified, say $201\times201$. The window is placed over and centred at pixel $(x,y)$ capturing the pixels $z_{i,j}$ for $x-100\leqslant i \leqslant x+100$ and $y-100\leqslant j \leqslant y+100$. The estimators $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ are the empirical null mean and standard deviation estimators, respectively, using the pixels captured in that window. This is then repeated for all $x$ and $y$. The $z$ statistics are then corrected using
\begin{equation}
	\zeta_{x,y} = 
	\dfrac{
		z_{x,y}-\widehat{\mu}_{0,x,y}
	}
	{
		\widehat{\sigma}_{0,x,y}
	}
\end{equation}
and only the corrected test statistics are used in the BH procedure.

@@

>>>>

The empirical null filter extends the empirical null to images. In this setting, the parameters of the null distribution varies spatially, slowly and smoothly in 2D space. Let $Z_{x,y}$ be the test statistic of the pixel at position $(x,y)$ for $x=1,2,\dotdotdot,W$ and $y=1,2,\dotdotdot,H$. Let each pixel have a test statistic distributed under the null such that
\begin{equation}
	Z_{x,y}|H_0\sim\normal\left(
		\mu_{x,y},\sigma_{0,x,y}^2
	\right)
	\ .
\end{equation}
Let the hypothesis
\begin{equation}
	H_0:\mu_{x,y}=\mu_{0,x,y}
\end{equation}
\begin{equation}
	H_1:\mu_{x,y}\neq\mu_{0,x,y}
\end{equation}
be tested for each pixel individually where $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively. Suppose $Z_{x,y}=z_{x,y}$ were observed for all $x$ and $y$. The empirical null filter aims to estimate the parameters $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ for all $x$ and $y$. This is so that inference can be done under the empirical null distribution.

The empirical null filter uses the empirical null on neighbouring pixels to estimate the null distribution parameters. For example to estimate $\mu_{0,x,y}$ and $\sigma_{0,x,y}$, a circular kernel of radius $r$ is centred at $(x,y)$. All the pixels captured in the circular kernel are then used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
\begin{equation}
	\widehat{\mu}_{0,x,y}
	=
	\widehat{\mu}_{0,x,y}
		\left(
			\text{all }z_{i,j}\text{ such that }(x-i)^2+(y-j)^2\leqslant r^2
		\right)
\end{equation}
and
\begin{equation}
	\widehat{\sigma}_{0,x,y}
	=
	\widehat{\sigma}_{0,x,y}
		\left(
			\text{all }z_{i,j}\text{ such that }(x-i)^2+(y-j)^2\leqslant r^2
		\right)
	\ .
\end{equation}
Using these estimates, the test statistics are then corrected using
\begin{equation}
	\zeta_{x,y} = 
	\dfrac{
		z_{x,y}-\widehat{\mu}_{0,x,y}
	}
	{
		\widehat{\sigma}_{0,x,y}
	}
\end{equation}
and only the corrected test statistics are used in hypothesis testing.

The critical parameter of choice is the kernel radius $r$. A $r$ too small will treat defects as the null and will not detect them. A $r$ too big can also cause problems as well. The empirical null filter does assume the null parameters vary smoothly and slowly so that the null test statistics captured by the kernel is somewhat Normal. If $r$ is too big, the kernel will capture far away test statistics with a very different null distribution. If all of these test statistics are pulled together into a histogram, the null distribution may not look Normal at all which can cause problems when fitting a Normal null distribution. Furthermore, if $r\rightarrow \infty$, then this is just using the empirical null on all pixels which is, as discussed before, not sensible.

$r$ does control the proportion of pixels which are null captured by the kernel, denoted as $\pi_0$. If the size of the defects are known, then $r$ should be selected such that
\begin{equation}
\dfrac{
	\text{area of defect}
}
{
	\pi r^2
}
\approx
5\% \text{ to } 10 \%
\end{equation}
so that $\pi_0$ is of a sensible value. In practice, the defects are unknown so various kernel radiuses should be tried out. But in general, the kernel radius should be much larger than the size of the defect.

The empirical null filter was implemented in an open source software called \texttt{ImageJ} \citep{abramoff2004image, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}, available on \texttt{GitHub} \citep{imagej2018rank}. This class implemented filters, such as the mean filter and median filter, using a circular kernel and multiple threads, making this a suitable framework for the empirical null filter. Figure \ref{fig:inference_fijiGui} shows the graphical user interface of the empirical null filter in \texttt{Fiji} \citep{schindelin2012fiji}, a distribution of \texttt{ImageJ}.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../figures/inference/fiji/gui.png}
    \caption{Graphical user interface of the empirical null filter in \texttt{Fiji}. The user can adjust the kernel radius as well as other advanced options relating to the Newton-Raphson method and the kernel density estimate. By products such as the empirical null parameters can be shown after the filtering as well.}
    \label{fig:inference_fijiGui}
\end{figure}

As a test, the empirical null filter with $r=5$ was used on a \texttt{ImageJ} sample image \texttt{bridge.gif}, as shown in Figure \ref{fig:inference_fijiBridgeFilter}. It is meaningless to use the empirical null filter on an image not for the purpose of the filter, however it does verify the filter works on arbitrary images. The empirical null images $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all ${x,y}$ could be of interest. In particular the empirical null mean image could be interpreted as the result of a mode filter \citep{griffin2000mean}. Figure \ref{fig:inference_fijiMean} compares the empirical null mean with other averaging filters. The empirical null mean creates an impasto look which is similar to the result in \cite{griffin2000mean}. Spread filters such as the standard deviation filter can be used to detect edges. Figure \ref{fig:inference_fijiStd} compares the standard deviation filter with the empirical null standard deviation. The resulting images are similar but it was notable that the edges in the empirical null standard deviation are sharper.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/bridge.png}
        \caption{Before filtering}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/bridgeFilter.png}
        \caption{After filtering}
    \end{subfigure}
    }
    \caption{Empirical null filter with $r=5$ on the sample image \texttt{bridge.gif}.}
    \label{fig:inference_fijiBridgeFilter}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/bridge.png}
        \caption{No filter}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/mean.png}
        \caption{Mean filter}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/median.png}
        \caption{Median filter}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/nullMean.png}
        \caption{Empirical null mean}
    \end{subfigure}
    }
    \caption{Various average filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}}
    \label{fig:inference_fijiMean}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/std.png}
        \caption{Standard deviation filter}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/nullStd.png}
        \caption{Empirical null standard deviation}
    \end{subfigure}
    }
    \caption{Various spread filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}.}
    \label{fig:inference_fijiStd}
\end{figure}

\subsection{Design and Implementation}

When using the the empirical null filter in \texttt{ImageJ}, the user is presented with a menu, as shown in Figure \ref{fig:inference_fijiGui}. Here the user can input the kernel radius, the filter then modifies the currently selected image $z_{x,y}$ to $\zeta_{x,y}$ for all $x$ and $y$ using a circular kernel with the specified radius. The menu also has options for by product images to be shown such as: the empirical null mean $\widehat{\mu}_{0,x,y}$, the empirical null standard deviation $\widehat{\sigma}_{0,x,y}$, the standard deviation filter, and quartile filters. Advanced options are available to the user. The number of initial values set the number of valid solutions required in the Newton-Raphson method on finding the mode of the density estimate. The user can also set the maximum number of steps and tolerance for the Newton-Raphson method. The bandwidth parameters for the kernel density estimate can also be adjusted here.

Because the empirical null filter was implemented by modifying the existing code in the class \texttt{RankFilters}, most of the design has already been done. \texttt{RankFilters} contain implementations of filters such as the mean filter and median filter. The implementation makes use of multiple threads, each thread filters a row in parallel. This is done by the following, a thread copies the value of each pixels in its current and neighbouring rows into a cache. Then for each column, the thread does its calculations using the cache then replaces the pixel value of the image to be filtered. Once the row has been filtered, the thread then moves onto the next unfiltered row.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
	    \begin{tabular}{lllllll}
	       $\ddots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\udots$ \\
	       $\cdots$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
	       $\cdots$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\ \cline{4-6}
	       $\cdots$ & $z_{1,1}$ & \multicolumn{1}{l|}{$z_{1,1}$} & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
	       $\cdots$ & $z_{2,1}$ & \multicolumn{1}{l|}{$z_{2,1}$}  & $z_{2,1}$ & $z_{2,2}$ & $\cdots$ \\
	       $\udots$ & $\vdots$ & \multicolumn{1}{l|}{$\vdots$}  & $\vdots$ & $\vdots$ & $\ddots$
		\end{tabular}
		\caption{Nearest pixel padding}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
	    \begin{tabular}{lllllll}
	       $\ddots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\udots$ \\
	       $\cdots$ & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & $\cdots$ \\
	       $\cdots$ & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & \texttt{NaN} & $\cdots$ \\ \cline{4-6}
	       $\cdots$ & \texttt{NaN} & \multicolumn{1}{l|}{\texttt{NaN}} & $z_{1,1}$ & $z_{1,2}$ & $\cdots$ \\
	       $\cdots$ & \texttt{NaN} & \multicolumn{1}{l|}{\texttt{NaN}}  & $z_{2,1}$ & $z_{2,2}$ & $\cdots$ \\
	       $\udots$ & $\vdots$ & \multicolumn{1}{l|}{$\vdots$}  & $\vdots$ & $\vdots$ & $\ddots$
		\end{tabular}
		\caption{\texttt{NaN} padding}
	\end{subfigure}
	\caption{When a kernel contain pixels outside the region of interest as shown by the solid line, the missing pixels can either be interpolated using the nearest pixel or completely ignored by filling in the missing pixels with \texttt{NaN}.}
	\label{fig:inference_padding}
\end{figure}

@@

\subsection{Real Data}
